---
title: "Positioning"
author: "Jelger Elings"
date: "2023-06-28"
output: html_document
editor_options: 
  markdown: 
    wrap: sentence
---


to fix:
 => fit_offset does not run. Needs latency object? 
  -> running SyncTagLatency shows latency object for 1 rec-pair only (62551-62552). Why not the others? 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, results = "hide")

require(kaltoa, quietly = T)
require(sf, quietly = T)
require(ggpot2, quietly = T)
require(stringr, quietly = T)

options(digits = 15)
```

Load metadata and get UTM projections of receiver locations.
It seems like one of our synchronization tags has an erroneous tag_ID.
From the vdat's and csv's it seems like tag_ID 62209 needs to be changed to 62920.

```{r, read receiver locations, echo=TRUE}
recs <- read.csv("./data/Receivers_IDs_locaties_deployment_2023.csv") %>%
  st_as_sf(coords = c('Long', 'Lat'), crs="EPSG:4326", remove=F) %>%
  st_transform(crs="EPSG:32632")
# Remove HR column
recs <-subset(recs, Detection.Type != "HR")
if (62209 %in% recs$Tag_ID) {
  recs[(recs$Tag_ID == 62209),]$Tag_ID <- 62920
}

fish.ids <- read.csv("./data/Tagged fish_2022.csv")
```


```{r, Add list of file names to metadata table}
files_df <- data.frame(file = dir(path = "./data/Detections/", pattern = "*.\\.csv"))
mtch <- stringr::str_match(files_df$file, "HR2-180 (\\d+)\\.csv")
files_df$Serial_number <- mtch[,2]

meta <- merge(files_df, recs, by = "Serial_number")
meta <- subset(meta, select = c("Serial_number", "file", "Tag_ID", "Full_Tag_ID", "geometry"))
meta
```

```{r, Loop through files, and create time filtered detections object for each receiver}
path <- "./data/Detections"

# times to filter
time_start <- as.POSIXct("01-05-2023", format="%d-%m-%Y", tz="UTC")
time_stop <- as.POSIXct("08-05-2023", format="%d-%m-%Y", tz="UTC")

# Save a list fo detections objects
dets <- list()
for(i in 1:nrow(meta)){
  print(meta$Serial_number[i])
  # load detections into temporary data.frame
  file = meta$file[i]
  tmp <- read.csv(paste(path, file, sep = '/'))
  
  # Find times of interest
  times <- as.POSIXct(tmp$Device.Time..UTC., format = "%Y-%m-%d %H:%M:%OS")
  idx <- which(times >= time_start & times <= time_stop)
  
  detect_times <- iso2DetectionTime(tmp$Device.Time..UTC.[idx])
  
  # ------ Save as detections object
  # Auxiliary data that might be interesting to keep
  df_aux = data.frame(
    db_signal = tmp$Signal.Strength..dB.[idx],
    db_noise = tmp$Noise..dB.[idx],
    quality = tmp$Quality.Score[idx])
  # Coordinate of receiver
  coord <- st_coordinates(meta$geometry[i])
  # Make detections object
  dets[[i]] <- Detections(
    detect_times = iso2DetectionTime(times[idx]), 
    detect_id = tmp$ID[idx], 
    type = tmp$Detection.Type[idx], 
    send_id = meta$Tag_ID[i], 
    x = coord[1], 
    y = coord[2], 
    sync_tags = meta$Tag_ID[i], 
    aux = df_aux)
}
rm(tmp)

# Convert list of Detections into a DetectionsList object
detlst <- do.call(DetectionsList, dets)
```

# Synchronizing the clocks

The clock synchronization will be done with HR pings only. 

```{r}
# Ignore (1) HR_self emissions, and (2) HR detections that match the IDs of sync tags.
detlst_filt <- subset(
  detlst, type != "HR_SELF" & !(type == "HR" & detect_id %in% meta$Tag_ID))
detlst <- detlst_filt

#detlst
plot(detlst_filt)

# Save as a RData file
saveRDS(object = detlst, file = "./Positioning_(James)_detlst.rds")
```

Before syncing, lets make a table showing the sync-tag detections across receiver pairs.
This will inform us for the sync-order specification. Receiver 62208's tag seems to have the best detections in the array. We'll use this as the central receiver

```{r include=TRUE}
SyncTagConnectivity(detlst)
```

```{r}
sync_order = data.frame(
  emit = c("62208"),
  detect = c("62207", "62211", "62552", "62553", "62920")#c("62206", "62207", "62208", "62211", "62551", "62552", "62553", "62920")
  )

# subset 24 hour of detections data
offset_times <- seq(as.POSIXct("2023-05-03 02:00:00"),
                    as.POSIXct("2023-05-04 02:00:00"),
                    by=3600)
detlst_24 <- subset(detlst, time >= offset_times[1] & time <= offset_times[length(offset_times)])


sync_model <- KaltoaClockSync(sync_order = sync_order,
                              min_interval = 270, max_interval = 330,
                              max_transmission_latency = 120,
                              clock_time = offset_times,
                              offset_max = 120)

int_drft <- init_drift(sync_model, detlst_24)
int_drft

drift(sync_model) <- int_drft$clock_drift

sync_fit <- fit_drift(sync_model,      
                      detlst_24,
                      cores = 4, iter = 4000)

plot(sync_fit)
rstan::traceplot(sync_fit@stan[[1]])

plot(detlst_24)
latency <- SyncTagLatency(detlst_24)
plot(SyncTagLatency(detlst = detlst_24))

fit_offsets(clocksync = sync_model, detlst = detlst_24)

detlst_corr <- synchronize(sync_fit, detlst_24) 
```
